### 2018-07-09 latex/results.tex
Resulst revision finished

A remaining puzzle was, why NADA is lost in vertebrates, while NADA and NamPRT both occur in bacteria. We tried to approach the puzzle with a competitive model with two compartments that share a Nam source. One compartment contains NADA while the other contains either NamPRT alone, or together with NNMT (for details, see experimental procedures and suppl. tab.~S2). Without NNMT, the compartment containing NADA shows slightly lower NAD consumption rates (fig.~\ref{fig:NNMT_comp_advantage}A), but is able to maintain much higher NAD concentrations at low cell division rates (fig.~\ref{fig:NNMT_comp_advantage}B). At high cell division rates, steady state concentrations in both compartments are similar. These comparable concentrations might explain why in bacteria that often have relatively high growth rates, both systems co-exist.

In the presence of NNMT, the NamPRT compartment has both higher NAD consumption rates and higher steady state NAD concentrations than the compartment containing NADA (fig.~\ref{fig:NNMT_comp_advantage}C and~D). The high NAD concentrations are dependent on a high affinity of NamPRT. When simulating a low affinity (high $K_{M}$) of NamPRT, the NADA compartment is able to maintain higher NAD concentrations although it still has a lower the NAD consumption flux. Taken together, the results suggest that the NADA pathway became less worthwhile when a higher affinity of NamPRT developed, possibly induced by NNMT.

>>>>

So far we have not discussed the effect of NADA on Nam-salvage and especially the question, why it is lost in vertebrates. As selection during evolution results usually from competition for resources, we built a two compartment model, based on the pathway model described above. One compartment contains NADA, while the other one contains either NamPRT alone, or together with NNMT. Both compartments share a limited  Nam source (for details, see experimental procedures and suppl. tab.~S2). Without NNMT, the compartment containing NADA shows slightly lower NAD consumption rates (fig.~\ref{fig:NNMT_comp_advantage}A), but is able to maintain much higher NAD concentrations especially at low cell division rates (fig.~\ref{fig:NNMT_comp_advantage}B). At high cell division rates, steady state concentrations in both compartments are similar. This might explain why in bacteria, that often have relatively high growth rates, both systems can co-exist.

In the presence of NNMT, the NamPRT compartment has both higher NAD consumption rates and higher steady state NAD concentrations than the compartment containing NADA (fig.~\ref{fig:NNMT_comp_advantage}C and~D). The higher NAD concentrations in the compartment containing NamPRT and NNMT can, however, only be maintained  if the affinity of NamPRT for Nam is high enough, corresponding to a low $K_{M}$. If the affinity of NamPRT is too low (high $K_{M}$), the NADA compartment is able to maintain higher NAD concentrations, but it still has a lower the NAD consumption flux.  Taken together, the results suggest that the NADA pathway might have become obsolete upon emergence of the  high affinity NamPRT This in turn might have been induced by the appearance of NNMT.
